---
title: "deneggs"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{deneggs}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

**deneggs is a package developed in the department of prevention and control of diseases transmitted by vector of the [Secretary of Health of Veracruz](https://www.ssaver.gob.mx/) and with colaboration of the [CENAPRECE](https://www.gob.mx/salud/cenaprece)**

# **overview**
**deneggs** is a package to generate predictive maps of the number of eggs or adults in areas where it is not collected.The predictive maps are generated using geostatistical analysis in the [INLA](http://www.r-inla.org/) framework. 

**deneggs** package has seven functions:

  - **`deneggs::spde_pred_map()`** generate the predictive map and calculate the hotspots. Run the models with six distributions.
  - **`deneggs::eggs_hotspots()`** generate the predictive map and calculate the hotspots. Run the model with one distribution.
  - **`deneggs::animap_vector_hotblocks()`** generate the animated map of hotblocks of eggs abundance.
  - **`deneggs::ovitraps_read()`** reads current ovitramp databases and historical.
  - **`deneggs::eggs_map()`** generates an entomological risk map or an egg density map.
  - **`deneggs::loc_grid_points()`** It is a complementary function that helps in the creation of grid of the locality in the prediction stack in [INLA](http://www.r-inla.org/).
  - **`mesh()`** It is a complementary function that helps in the creation of mesh.
  
## Instalation

```{r setup}
library(deneggs)
```

## Development version

To get a bug fix, or use a feature from the development version, you can
install deneggs from GitHub.

``` r
# install.packages("devtools")
devtools::install_github("fdzul/deneggs")
remotes::install_github("fdzul/deneggs")
``` 

```{r example, dpi = 300, warning=FALSE, fig.align = "center", message=FALSE,}
# Step 1. define the paths 
library(magrittr)
library(sf)
path_lect <- "C:/Users/felip/Dropbox/cenaprece_datasets/12_Guerrero"
path_coord <- paste(path_lect,"DescargaOvitrampasMesFco.txt", sep = "/")

acapulco <- deneggs::spde_pred_map(path_lect = path_lect,
                                   cve_ent = "12",
                                   locality  = c("Acapulco de Juárez"),
                                   path_coord =  path_coord,
                                   longitude  = "Pocision_X",
                                   latitude =  "Pocision_Y",
                                   aproximation = "gaussian",
                                   integration = "eb",
                                   k = 20,
                                   palette_vir  = "magma",
                                   leg_title = "Huevos",
                                   week = lubridate::epiweek(Sys.Date())-1,
                                   plot = TRUE,
                                   var = "Huevecillos",
                                   cell_size = 1000,
                                   alpha = .99)


knitr::kable(head(acapulco$data), "simple")

knitr::kable(head(acapulco$pred), "simple")

knitr::kable(head(acapulco$dics), "simple")

knitr::kable(head(acapulco$hotspots), "simple")

# The locality limit of Acapulco
plot(sf::st_geometry(acapulco$loc))

# prediction of the number of Ae. aegypty eggs in the metropolitan area of Acapulco
acapulco$map

# prediction of the number of eggs in the metropolitan area of Monterrey 
deneggs::eggs_hotspots(path_lect = "C:/Users/felip/Dropbox/cenaprece_datasets/19_nuevo_leon",
                       cve_ent = "19",
                       locality  = c("Ciudad General Escobedo", "Ciudad Apodaca",
                                     "Guadalupe", "Monterrey", "Ciudad Santa Catarina",
                                     "San Pedro Garza García", "Ciudad Benito Juárez",
                                     "San Nicolás de los Garza", "Montebello"),
                       path_coord =  "C:/Users/felip/Dropbox/cenaprece_datasets/19_nuevo_leon/DescargaOvitrampasMesFco.txt",
                       longitude  = "Pocision_X",
                       latitude =  "Pocision_Y",
                       aproximation = "gaussian",
                       integration = "eb",
                       fam = "zeroinflatednbinomial1",
                       k = 30,
                       palette_vir  = "magma",
                       leg_title = "Huevos",
                       plot = FALSE,
                       hist_dataset = FALSE, #####
                       sem = lubridate::epiweek(Sys.Date())-2,
                       var = "eggs",
                       cell_size = 1000,
                       alpha = .99)$map

# prediction of the number of eggs in the metropolitan area of Merida
deneggs::eggs_hotspots(path_lect = "C:/Users/felip/Dropbox/cenaprece_datasets/31_yucatan",
                       cve_ent = "31",
                       locality  = c("Mérida"),
                       path_coord =  "C:/Users/felip/Dropbox/cenaprece_datasets/31_yucatan/DescargaOvitrampasMesFco.txt",
                       longitude  = "Pocision_X",
                       latitude =  "Pocision_Y",
                       aproximation = "gaussian",
                       integration = "eb",
                       fam = "zeroinflatednbinomial1",
                       k = 30,
                       palette_vir  = "magma",
                       leg_title = "Huevos",
                       plot = FALSE,
                       hist_dataset = FALSE, #####
                       sem = lubridate::epiweek(Sys.Date())-2,
                       var = "eggs",
                       cell_size = 1000,
                       alpha = .99)$map

# prediction of the number of eggs in the metropolitan area of Guadalajara
deneggs::eggs_hotspots(path_lect = "C:/Users/felip/Dropbox/cenaprece_datasets/14_jalisco",
                       cve_ent = "14",
                       locality  = c("Guadalajara", "Tlaquepaque", "Zapopan", "Tonalá"),
                       path_coord =  "C:/Users/felip/Dropbox/cenaprece_datasets/14_jalisco/DescargaOvitrampasMesFco.txt",
                       longitude  = "Pocision_X",
                       latitude =  "Pocision_Y",
                       aproximation = "gaussian",
                       integration = "eb",
                       fam = "zeroinflatednbinomial1",
                       k = 40,
                       palette_vir  = "magma",
                       leg_title = "Huevos",
                       plot = FALSE,
                       hist_dataset = FALSE, #####
                       sem = lubridate::epiweek(Sys.Date())-2,
                       var = "eggs",
                       cell_size = 1000,
                       alpha = .99)$map
```

