---
title: "eggs prediction week"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{eggs_prediction_week}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}
library(deneggs)
```

La predicción de huevos en toda la localidad, es decir tanto en las área muestreadeas como en las áreas no muestreadas (el análisis geoestadístico), se realiza con la funcion ***[deneggs::spde_pred_map](https://github.com/fdzul/deneggs/blob/master/R/spde_pred_map.R)***, la función ***[deneggs::eggs_hotspots](https://github.com/fdzul/deneggs/blob/master/R/eggs_hotspots.R)***, y [deneggs::eggs_hotspots_week](https://github.com/fdzul/deneggs/blob/master/R/eggs_hotspots.R)

Ambas funciones tienen argumentos similares, excepto por el año y la semana. La primera funciona para


### **`deneggs::spde_pred_map()`** return a list with six object:

 - **`data`** is the original dataset of the ovitrap.
 - **`pred`** is the predicction dataset of *the Ae. aegypti* eggs.
 - **`dics`** is a dataframe with the dics of six distribution (poisson, zeroinflatedpoisson0, 1, zeroinflatedpoisson1, nbinomial, nbinomial2, zeroinflatednbinomial0, zeroinflatednbinomial1).
 - **`hotspots`** a dataset with the eggs prediction and the hotspots eggs.
 - **`loc`** is the boundary locality.
 - **`map`** is the map prediction.
 
 
 
